EdEntrePres

### 2014-12-02 EdEntrePres.Rmd
Maps, new data cleaning
Indicated where we are stuck
Fixed the avg figure for presentation

## Education to Entrepreneurship

@@

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

@@

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

>>>>

## Education -> Entrepreneurship

## Different Country-level Perceptions of Good Opportunities to Start a Business

@@

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")

@@

## Distribution of Perception Differences

```{r}
hist(D4$mean)

```
## Slide with R Code and Output
